# chapter 2 regression and model validation

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.

*Read the file "learning2014.txt produced from the data wrangling step. The data from includes 166 observations and 7 variables. This dataset reflects the survey of approaches of learning and how they effect the exam points of individuals.*
```{r}
date()
learning2014<-read.table("learning2014.txt",header = TRUE,sep = " ")
str(learning2014)
```

*a graphical overview of the data. The overview is showing how two of the variables related to each other.
```{r}
library(GGally)
library(ggplot2)
# from this overview, we can see that the age of the individuals are skewed to younger individuals, and attitute and 
p <- ggpairs(learning2014, mapping = aes(), lower = list(combo = wrap("facethist", bins = 20)))



#multiple regression with 3 variables
my_model<-lm(points~attitude+stra+surf,data = learning2014)
summary(my_model)

# remove a variable with low statistical significance 
my_model2<-lm(points~attitude+stra,data = learning2014)
summary(my_model2)
par(mfrow=c(2,2))
plot(my_model2,which = c(1,2,5))
```